---
title: "Eva Goljat - week 1 Exercise part B"
format: html
editor: visual
---

### Starting up

Install and load all the neccessary packages

```{r}
library(ggplot2) 
library(tidyverse) 
library(palmerpenguins)
```

### Creating the data

Using the rlnorm function create values belonging to "a". The chosen mean was 5 and standard deviation was 0,5.

```{r}
a <- rlnorm(n = 100, meanlog = 5, sdlog = 0.5)
```

Using the function **data.frame,** create a dataframe called **data**, where you collected all values in a.

```{r}
data = data.frame(value=a)
```

### Visualization

Using the function **ggplot** create a basic histogram called hg.

```{r}
hg <- ggplot(data, aes(x=value)) +
  geom_histogram(bins = 100, fill = 'sienna3', color = 'sienna') +
  ggtitle("Histogram - linear scale")
hg
```

Using the ggplot create a basic histogram with a logarithmic scale (named lg), determined with function scale_x_log10.

```{lg <- ggplot(data, aes(log(x=value))) +}
  geom_histogram(bins = 100, fill = 'sienna1', color = 'sienna') +
  scale_x_log10() +
  ggtitle("Histogram - log scale")
lg 
```

We will now create a violin plot called vp, what has values on the x-axis and the for the y axis we only put 1.

```{r}
vp <- ggplot(data, aes(x = value, y = log_value)) +
  geom_violin(fill = "thistle3", color = "plum4") +
  geom_boxplot(width = 0.1, fill = "pink1", color = "orchid4") +
  labs(y = "Log-Transformed Value") +
  ggtitle("Violin Plot")
vp
```

### Final comments

In all honesty R is not my strength and I am still far from fully understanding how certain functions work. The weakest point in this exercise is the violin plot.
